%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {RESEARCHER AND SOFTWARE DEVELOPER} % Job title
    {Teseo Srl} % Organization
    {Genova, Italy} % Location
    {Jun. 2018--Now} % Date(s)
    {
      \begin{cvparagraph}
      Development of ambient intelligence solutions for the Kibi project: indoor localization and monitoring for elderly care applications with embedded wearable devices.
      \end{cvparagraph}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed an Android WearOS application for elderly care monitoring, main features: indoor localization (BLE + Neural network classifier), fall detection, inactivity detection, device authentication and management trough RESTful API}
        \item {Designed, implemented and tested a fall detection algorithm based on inertial and barometric pressure data}
        \item {Developed a mobile Android application in Kotlin as a user companion app for system management}
        \item {Defined the technical specifications of a custom embedded board intended as a wearable smartwatch}
        \item {
          Developed a prototype firmware enabling a fall detection algorithm on the custom board: based on a STM32 ARM Cortex-M4/M0 dual core microcontroller
        }
        \item{Developed a simple driver for an SRAM module}
        \item{Debugging and testing of the prototype firmware, participated to the opensource debugging of ST peripheral drivers} 
      \end{cvitems}
    }
  %-----------------------------------------------------------------------------------------
  \cventry
    {RESEARCHER, AERIAL ROBOTICS} % Job title
    {Università degli studi di Genova} % Organization
    {Genova, Italy} % Location
    {Feb. 2016 – Feb. 2018} % Date(s)
    {
      \begin{cvparagraph}
      My work was conducted in the context of the Italian project MAREA, a consortium of universities and companies working on robots cooperation and management under search and rescue scenarios.
      \end{cvparagraph}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a software, written in C++ under Linux environment, for managing general flight missions}
        \item {Designed and integrated a task for  automatic landing on a floating and moving platform}
        \item {Integration of a companion computer (Raspberry Pi 3) with the PixHawk flight controller}
        \item {Supervised master students for group projects, co-supervised 2 bachelor thesis and one master thesis}
     \end{cvitems}
    }

%-----------------------------------------------------------------------------------------
  \cventry
    {TEACHING ASSISTANT} % Job title
    {Università degli studi di Genova} % Organization
    {Genova, Italy} % Location
    {Sep. 2017–Now} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Teaching and conducting lab sessions on Robot Programming to master students. Main topics are: ROS programming and GazeboSim}
        \item {Teaching and conducting lab sessions on C++ to bachelor students}
      \end{cvitems}
    }

    \cventry
    {MASTER THESIS: algorithms for controlling and tracking UAVs in indoor scenarios} % Job title
    {Università degli studi di Genova} % Organization
    {Genova, Italy} % Location
    {Mar. 2014–Oct. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Integration of an Optitrack motion capture system with the PX4 autopilot estimation algorithms}
        \item {Contributed to the development of the motion capture position estimation module of the PX4 open source autopilot}
        \item {Development of a Qt ground station enabling the robot to perform lists of tasks in an autonomous way}
        \item {Design and testing of an algorithm for automatic landing on moving targets}
      \end{cvitems}
    }
%------------------------------------------------------------------------
  \cventry
    {MANAGEMENT STAFF @ EFMC9 CONFERENCE} % Job title
    {Università degli studi di Roma Tor Vergata} % Organization
    {Roma, Italy} % Location
    {Sep. 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Worked as part of the organizing staff at the 9th European Fluid Mechanics Conference}
      \end{cvitems}
    }

\end{cventries}
