%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{About me}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}
    Motivated roboticist with an international background. Multidisciplinarity, as being able to jump from one field to another, is the main characteristic I developed since the beginning of my academic studies.
    Thanks to that I have been able to explore horizontally a broad set of disciplines where I streghtened the ability of viewing problems from different angles. My professional career started as a researcher in aerial robotics, studying and implementing techniques for autonomous landing on unpredictable moving objects. 
    During this period I've matured a deep understanding of mathematical modeling, C++ programming and a good set of technical skills involving the deployment of an application running as a companion to the PX4 Autopilot firmware. 
    Later in my career I started to work in a startup where I currently occupy a software developer position. In this reality I have been contributing to the development of a smart solution for elderly care monitoring and assistance. I gained experience in Android development, under which I desinged a wearable application capable of running algorithms in order to support 
    medical staff in dealing with patients in home care facilities. I also gained experience and lots of interest in embedded system design and firmware development. For this job I was able to fully exploit my multidisciplinary background due to the nature of the dynamical environment startups usually consist of.
    My past experiences made me a fast and keen learner, I am eager to expand my education, with the help of others, in embedded system development and Real Time Systems design for the future of my career.
\end{cvparagraph}
