%-------------------------------------------------------------------------------
%  SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Education}

%-------------------------------------------------------------------------------
%  CONTENT
%-------------------------------------------------------------------------------

\cvsubsection{Academic Qualifications}

\begin{cventries}

  \cventry
  {M.Sc. in Robotics Engineering –- EMARO (European Master on Advanced Robotics)} % Degree
  {École Centrale de Nantes (Year 1), Università degli Studi di Genova (Year 2)} % Institution
  {Nantes, France; Genova, Italy} % Location
  {Sept. 2013 -- Oct. 2015} % Date(s)
  {
    \begin{cvitems}
    \item {Double-degree program, ranked 1st in class.}
    \item {Specialization in control, estimation, AI, and robotics systems design.}
    \item {Master thesis: indoor UAV control and tracking –- integrated OptiTrack motion capture into PX4 estimation stack, contributed to the PX4 open‑source position estimator, developed a Qt ground station, and implemented autonomous landing on moving targets.}
    \end{cvitems}
    \begin{cvparagraph}
      Gained hands-on experience in mobile robotics, path planning, optimization, embedded systems, and nonlinear system analysis.
    \end{cvparagraph}
  }

  \cventry
  {B.Sc. in Engineering Sciences} % Degree
  {Università di Roma Tor Vergata} % Institution
  {Rome, Italy} % Location
  {Sept. 2010 -- Oct. 2013} % Date(s)
  {
    \begin{cvitems}
    \item {Graduated with 110/110 cum laude.}
    \item {First English-taught engineering program in Italy.}
    \item {Focus on scientific fundamentals and mechatronics.}
    \end{cvitems}
    \begin{cvparagraph}
      Solid background in mathematics, physics, mechanics, and electronics.
    \end{cvparagraph}
  }

\end{cventries}

%-------------------------------------------------------------------------------
\cvsubsection{Additional Training}

\begin{cventries}

  \cventry
  {Certificates: Embedded Systems and Robotics} % Title
  {} % Institution
  {} % Location
  {} % Date(s)
  {
    \begin{cvitems}
    \item {\textbf{ARM Cortex-M Programming} –- Doulos (Jun 2021) \underline{\href{https://shorturl.at/opCKZ}{Certificate link}}}
      \begin{cvparagraph}
        Focused on ARM Cortex-M4 programming, including peripherals, interrupts, and low-power modes.
      \end{cvparagraph}
    \item {\textbf{FreeRTOS Training} –- Doulos (Dec 2020) \underline{\href{https://bit.ly/3ppdcOF}{Certificate link}}}
      \begin{cvparagraph}
        Covered FreeRTOS architecture, task management, inter-task communication, and synchronization.
      \end{cvparagraph}
      % \item {\textbf{Ethereum/Hyperledger Dev} –- B9Lab (Oct 2018) \href{https://bit.ly/2ExiR1h}{[Eth]} \href{https://bit.ly/2R4wjk4}{[Hyp]}}
    \end{cvitems}
  }

  \cventry
  {Summer Schools} % Title
  {} % Institution
  {} % Location
  {2015--2017} % Date(s)
  {
    \begin{cvitems}
    \item {RegML PhD Course –- Machine Learning theory and regularization, Genova, Italy}
    \item {TRADR/EuRathlon –- Aerial/ground cooperative robotics, Oulu, Finland}
    \item {TRADR MAV School –- Modeling, control, and estimation for aerial robotics}
    \end{cvitems}
  }

\end{cventries}
