%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  \cventry
    {Senior C++ Software Developer} % Job title
    {Luxoft} % Organization
    {Turin, Italy} % Location
    {Jan. 2022 -- Apr. 2024} % Date(s)
    {
      \begin{cvparagraph}
        Contributed to the development of perception software for a major European automotive OEM in the autonomous driving domain. Focused on core perception algorithms and the design of a scalable Software-in-the-Loop (SIL) framework for testing and debugging.
      \end{cvparagraph}
      \vspace{1em}
      \begin{cvitems}
        \item {Owned and maintained the lane estimation module, driving enhancements in performance and reliability.}
        \item {Designed and implemented the SIL framework for functional debugging and CI-based KPI/test automation.}
        \item {Collaborated across teams to ensure seamless integration of perception features and testing infrastructure.}
        \item {Led technical planning to achieve team OKRs and supported feature delivery and defect resolution.}
        \item {\textbf{Technologies:} Modern C++ (C++14/17), Test-Driven Development, Bazel, Sensor Fusion, State Estimation}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Researcher and Software Developer} % Job title
    {Teseo Srl} % Organization
    {Genova, Italy} % Location
    {Jun. 2018 -- Jan. 2022} % Date(s)
    {
      \begin{cvparagraph}
        Developed embedded and mobile solutions for the Kibi project, an ambient intelligence system for elderly care involving wearable devices and indoor localization.
      \end{cvparagraph}
      \vspace{1em}
      \begin{cvitems}
        \item {Built Android WearOS and Kotlin mobile applications with BLE localization and REST API integration.}
        \item {Designed fall detection using IMU and pressure sensors, implemented on custom STM32-based hardware.}
        \item {Defined system architecture and developed low-level firmware with driver integration and debugging.}
      \end{cvitems}
    }

%-----------------------------------------------------------------------------------------
  \cventry
    {Researcher, Aerial Robotics} % Job title
    {Università degli Studi di Genova} % Organization
    {Genova, Italy} % Location
    {Feb. 2016 -- Feb. 2018} % Date(s)
    {
      \begin{cvparagraph}
        Worked on the MAREA project focused on multi-robot coordination for search and rescue missions.
      \end{cvparagraph}
      \vspace{1em}
      \begin{cvitems}
        \item {Developed mission control software in C++ for aerial platforms running Linux.}
        \item {Implemented autonomous landing on floating platforms using onboard sensing.}
        \item {Integrated companion computing using Raspberry Pi and PixHawk flight controllers.}
        \item {Supervised and mentored students on research and thesis projects.}
      \end{cvitems}
    }

%-----------------------------------------------------------------------------------------
  \cventry
    {Teaching Assistant} % Job title
    {Università degli Studi di Genova} % Organization
    {Genova, Italy} % Location
    {Sep. 2017 -- 2020} % Date(s)
    {
      \begin{cvitems}
        \item {Conducted lab sessions on Robot Programming for master's students using ROS and Gazebo.}
        \item {Led introductory C++ programming labs for undergraduate students.}
      \end{cvitems}
    }

%-----------------------------------------------------------------------------------------
  \cventry
    {Conference Staff – EFMC9} % Job title
    {Università degli Studi di Roma Tor Vergata} % Organization
    {Rome, Italy} % Location
    {Sep. 2012} % Date(s)
    {
      \begin{cvitems}
        \item {Supported organization and logistics for the 9th European Fluid Mechanics Conference.}
      \end{cvitems}
    }

\end{cventries}
